### 2024-09-25 paper/paper.qmd
Update

---
title: "Data Analysis of Toronto Beach Data"
author: "Yanzun Jiang"
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

We use @citeR and @opendatatoronto.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
# 
# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

```

\newpage

# References

### 2024-09-26 paper/paper.qmd
Update

@@
 ---
-title: "Data Analysis of Toronto Beach Data"
+title: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls at Beaches in Toronto"
 author: "Yanzun Jiang"
-thanks: "Code and data are available at: LINK."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+thanks: "Code and data supporting this analysis is available at: https://github.com/Stary54264/Toronto-Beach-Data"
+abstract: "This paper conducted a basic data analysis on data of beaches in Toronto.
+The variables mentioned in the tile are highly correlated.
+The analysis can help us to know better about beaches in Toronto.
+Further, it helps meteorologists to monitor climate changes."
 format: pdf
@@
 
+# load packages and read data
 library(tidyverse)
-library(palmerpenguins)
+library(knitr)
 ```
@@
 
-The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows.
+
+@sec-data
+
+&nbsp; @sec-data-1
+
+&nbsp; @sec-data-2
+
+&nbsp; &nbsp; @sec-data-2-1
+
+&nbsp; &nbsp; @sec-data-2-2
+
+&nbsp; &nbsp; @sec-data-2-3
+
+&nbsp; &nbsp; @sec-data-2-4
+
+@sec-results
+
+@sec-discussion
+
+\newpage
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+```
+
+## Preview of data {#sec-data-1}
+
+Our data (@tbl-data) is about beaches in Toronto, from @opendatatoronto.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: tbl-data
 #| echo: false
@@
 
-# analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-# 
-# analysis_data |> 
-#   ggplot(aes(x = width, y = length)) +
-#   geom_point(alpha = 0.8) +
-#   theme_minimal() +
-#   labs(x = "Wing width (mm)",
-#        y = "Wing length (mm)")
+kable(head(data), format = "markdown")
 ```
 
-Talk way more about it.
+This dataset records the date (which was separated into year, month, and day), the air temperature, whether it rains or not, the water temperature, and the observations of water fowls.
+We will analyze the relationship between these variables in the following part.
 
-# Model
+## Visualization of the Distribution of Each Observed Variable {#sec-data-2}
 
-The goal of our modelling strategy is twofold. Firstly,...
+This part shows the distributions of each observed variables using histograms.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+### Air Temperature {#sec-data-2-1}
 
-## Model set-up
+This histogram (@fig-air-temp) shows the distribution of air temperatures of beaches in Toronto.
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+```{r}
+#| label: fig-air-temp
+#| fig-cap: Histogram of Air Temperature
+#| echo: false
+#| warning: false
+#| message: false
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+data |>
+  ggplot(aes(x = air_temp)) +
+  geom_histogram(bins = 30, col = "darkblue", fill = "lightblue") +
+  theme_minimal() +
+  labs(x = "Air Temperature", y = "# of Occurences")
+```
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We can clearly see the data is unimodal and is not skewed.
 
-### Model justification
+### Rain {#sec-data-2-2}
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+This bar graph (@fig-rain) shows the distribution of whether it rains of not at beaches in Toronto.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+```{r}
+#| label: fig-rain
+#| fig-cap: Bar Graph of Whether It Rains or Not
+#| echo: false
+#| warning: false
+#| message: false
 
-# Results
+data |>
+  ggplot(aes(x = rain)) +
+  geom_bar(col = "darkblue", fill = "lightblue") +
+  theme_minimal() +
+  labs(x = "Whether It Rains or Not", y = "# of Occurences")
+```
 
-Our results are summarized in @tbl-modelresults.
+We can clearly see that there are less raining days.
+
+### Water Temperature {#sec-data-2-3}
+
+This histogram (@fig-water-temp) shows the distribution of water temperatures of beaches in Toronto.
+
+```{r}
+#| label: fig-water-temp
+#| fig-cap: Histogram of Water Temperature
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = water_temp)) +
+  geom_histogram(bins = 30, col = "darkblue", fill = "lightblue") +
+  theme_minimal() +
+  labs(x = "Water Temperature", y = "# of Occurences")
+```
+
+We can clearly see the data is unimodal, which is the same as air temperatures, but it is left-skewed.
+
+### Observations of Water Fowls {#sec-data-2-4}
+
+This histogram (@fig-water-fowl) shows the distribution of observations of water fowls of beaches in Toronto.
+
+```{r}
+#| label: fig-water-fowl
+#| fig-cap: Histogram of Observations of Water Fowls
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = water_fowl)) +
+  geom_histogram(bins = 30, col = "darkblue", fill = "lightblue") +
+  theme_minimal() +
+  labs(x = "Observations of Water Fowls", y = "# of Occurences")
+```
+
+We can clearly see the data is unimodal but highly right-skewed.
+
+# Results {#sec-results}
+
+Our results are summarized in.
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-```
-
 \newpage

### 2024-09-26 scripts/00-simulate_data.R
Added More Comments for Reproducibility

@@ -22,6 +22,7 @@ end_date <- as.Date("2023-12-31")
 # Set the number of observations
 sim <- 1000
 
+# Simulate the data
 data <-
   tibble(
     date = as.Date(

### 2024-09-26 scripts/01-download_data.R

@@ -14,16 +14,16 @@ library(tidyverse)
 
 
 #### Download data ####
-# get package
+# Get package
 package <- show_package("toronto-beaches-observations")
 
-# get all resources for this package
+# Get all resources for this package
 resources <- list_package_resources("toronto-beaches-observations")
 
-# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
+# Identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
 datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
 
-# load the first datastore resource as a sample
+# Load the first datastore resource as a sample
 data <- filter(datastore_resources, row_number()==1) %>% get_resource()
 
 

### 2024-09-26 scripts/02-data_cleaning.R

@@ -13,8 +13,10 @@ library(tidyverse)
 
 
 #### Clean data ####
+# Read the data
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 
+# Basic cleaning of the data
 cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
@@ -27,7 +29,7 @@ cleaned_data <-
   mutate(date = lubridate::ymd(paste(year, month, day, sep = "-"))
   )
 
-# Remove outliers
+# Get expected values and standard deviations
 mean_air_temp <- mean(cleaned_data$air_temp)
 sd_air_temp <- sd(cleaned_data$air_temp)
 mean_water_temp <- mean(cleaned_data$water_temp)
@@ -35,6 +37,7 @@ sd_water_temp <- sd(cleaned_data$water_temp)
 mean_water_fowl <- mean(cleaned_data$water_fowl)
 sd_water_fowl <- sd(cleaned_data$water_fowl)
 
+# Remove the outliers using z-scores
 cleaned_data <-
   cleaned_data |>
   filter(abs((air_temp - mean_air_temp) / sd_air_temp) < 3,

### 2024-09-26 scripts/03-test_data.R

@@ -13,6 +13,7 @@ library(tidyverse)
 
 
 #### Test data ####
+# Read the data
 data <- read_csv("data/raw_data/simulated.csv")
 
 # Test for negative water temperature

### 2024-09-26 paper/paper.qmd
Appendix Completed

@@
 ---
-title: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls at Beaches in Toronto"
+title: "Toronto Beach Data"
+subtitle: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls"
 author: "Yanzun Jiang"
@@
 @sec-data
-
-&nbsp; @sec-data-1
-
-&nbsp; @sec-data-2
-
-&nbsp; &nbsp; @sec-data-2-1
-
-&nbsp; &nbsp; @sec-data-2-2
-
-&nbsp; &nbsp; @sec-data-2-3
-
-&nbsp; &nbsp; @sec-data-2-4
-
+@sec-data-1
+@sec-data-2
+@sec-data-2-1
+@sec-data-2-2
+@sec-data-2-3
+@sec-data-2-4
 @sec-results
-
 @sec-discussion
-
-\newpage
 
@@
 #| label: tbl-data
+#| tbl-cap: Preview of Data
 #| echo: false
@@
 #| label: fig-air-temp
-#| fig-cap: Histogram of Air Temperature
+#| fig-cap: Air Temperature at Toronto Beaches from
 #| echo: false
@@
 
-# Appendix {-}
+# Appendix {#sec-appendix}
 
-# Additional data details
+## Dataset and Graph Sketches {#sec-appendix-1}
+
+Sketches depicting both the desired dataset and the graphs generated in this analysis are available in the GitHub Repository.
+
+## Data Cleaning {#sec-appendix-2}
+
+The data cleaning process involved renaming variables, filtering out useless columns from the raw dataset, filtering out observations with NAs, and removing the outliers using z-scores.
 

### 2024-09-26 paper/paper.qmd
Introduction Completed

@@
 date-format: long
-thanks: "Code and data supporting this analysis is available at: https://github.com/Stary54264/Toronto-Beach-Data"
-abstract: "This paper conducted a basic data analysis on data of beaches in Toronto.
-The variables mentioned in the tile are highly correlated.
-The analysis can help us to know better about beaches in Toronto.
-Further, it helps meteorologists to monitor climate changes."
+thanks: "Code and data supporting this analysis is available at: <https://github.com/Stary54264/Toronto-Beach-Data>"
+abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, rainfall, and waterfowl observations.
+The findings reveal that ?increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings?.
+These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
+Future research should explore the impact of these environmental factors on beachgoer experiences and the broader ecological implications."
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
+\newpage
+
 # Introduction
 
-We use @citeR and @opendatatoronto.
+In 2014, Toronto experienced an extremely cold summer that impacted its beaches @torontoweather.
+During this period, data on key environmental factors, such as air temperature, water temperature, rainfall, and observations of waterfowl activity, was collected at various beaches across the city @opendatatoronto.
+These factors are critical as they directly influence the ecological balance of the beaches, the safety of recreational activities, and the overall enjoyment of beachgoers @weatherandbeach.
 
-The remainder of this paper is structured as follows.
+Consequently, analyzing this environmental data is essential to understanding how these variables affect the behavior of waterfowl and the suitability of the beaches for public use.
+According to @temperatureandwaterfowl, waterfowl presence can be influenced by temperature changes, precipitation, and human activity on the beaches.
+This study focuses on examining the relationships between air temperature, water temperature, rainfall, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.
 
-@sec-data
-@sec-data-1
-@sec-data-2
-@sec-data-2-1
-@sec-data-2-2
-@sec-data-2-3
-@sec-data-2-4
-@sec-results
-@sec-discussion
+To conduct this analysis, a dataset collected by @opendatatoronto was utilized, as described in @sec-data.
+Based on the initial findings, it was observed that ???higher water temperatures coincided with an increase in waterfowl activity, while rainy days led to a decrease in sightings ???(@sec-results).
+As discussed in @sec-discussion, ???these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness.
+Further recommendations include improving public awareness of how wildlife interactions and weather patterns influence beach environments???.
+This paper's structure includes an overview of the data and methods in @sec-data, the results of the analysis in @sec-results, a detailed discussion of the results in @sec-discussion, and supplementary insights in @sec-appendix.
 
@@
 
-## Preview of data {#sec-data-1}
+## Overview
+
+### Preview of the Dataset
 
@@
 
-## Visualization of the Distribution of Each Observed Variable {#sec-data-2}
-
-This part shows the distributions of each observed variables using histograms.
-
-### Air Temperature {#sec-data-2-1}
+### Air Temperature
 
@@
 
-### Rain {#sec-data-2-2}
+### Rain
 
@@
 
-### Water Temperature {#sec-data-2-3}
+### Water Temperature
 
@@
 
-### Observations of Water Fowls {#sec-data-2-4}
+### Observations of Water Fowls
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-## Dataset and Graph Sketches {#sec-appendix-1}
+## Graph and Sketches
 
@@
 
-## Data Cleaning {#sec-appendix-2}
+## Data Cleaning
 

### 2024-09-26 paper/paper.qmd
Update

@@
 title: "Toronto Beach Data"
-subtitle: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls"
+subtitle: "Data Analysis of the Relationship Between Date of Observation, Air Temperatures, Water Temperatures, Rainfall Presence, and waterfowl activity"
 author: "Yanzun Jiang"
@@
 abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, rainfall, and waterfowl observations.
-The findings reveal that ?increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings?.
-These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
+The findings reveal that #TODO increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings.# These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
 Future research should explore the impact of these environmental factors on beachgoer experiences and the broader ecological implications."
@@
 According to @temperatureandwaterfowl, waterfowl presence can be influenced by temperature changes, precipitation, and human activity on the beaches.
-This study focuses on examining the relationships between air temperature, water temperature, rainfall, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.
+This study examines the relationships between air temperature, water temperature, rainfall, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.
 
 To conduct this analysis, a dataset collected by @opendatatoronto was utilized, as described in @sec-data.
-Based on the initial findings, it was observed that ???higher water temperatures coincided with an increase in waterfowl activity, while rainy days led to a decrease in sightings ???(@sec-results).
-As discussed in @sec-discussion, ???these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness.
-Further recommendations include improving public awareness of how wildlife interactions and weather patterns influence beach environments???.
-This paper's structure includes an overview of the data and methods in @sec-data, the results of the analysis in @sec-results, a detailed discussion of the results in @sec-discussion, and supplementary insights in @sec-appendix.
+Based on the initial findings, it was observed that #TODO higher water temperatures coincided with an increase in waterfowl activity, while rainy days led to a decrease in sightings (@sec-results).# As discussed in @sec-discussion, #TODO these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness.
+Further recommendations include improving public awareness of how wildlife interactions and weather patterns influence beach environments.# This paper's structure includes an overview of the data and methods in @sec-data, the results of the analysis in @sec-results, a detailed discussion of the results in @sec-discussion, and supplementary insights in @sec-appendix.
 
@@
 
+The dataset used in this analysis is the "Toronto Beaches Observations" sourced from Toronto's Open Data platform @opendatatoronto.
+It records various aspects of the beaches in Toronto from 2008 to present.
+In Toronto, water quality at beaches is regularly monitored to ensure public safety, and environmental variables, such as air and water temperature, rainfall, and the presence of waterfowl, are tracked for ecological and recreational purposes @opendatatoronto.
+
+The variables analyzed in this study include "Date," which records the day each measurement was taken; "Air Temperature," which represents the temperature of the atmosphere at the beach site; "Water Temperature," indicating the temperature of the water in designated swimming areas; "Rainfall," which notes whether there was precipitation on the day of observation; and "Waterfowl Observations," which track the number of birds spotted near the water @opendatatoronto.
+
+The dataset was accessed using the `opendatatoronto` package @opendatatoronto.
+For the analysis, the R programming language was employed @citeR, utilizing the `tidyverse` @citetidyverse package for data cleaning, transformation, visualization, and the `janitor` package @citejanitor for initial cleaning and formatting of the raw data.
+Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package @citetidyverse.
+
 ### Preview of the Dataset
 
-Our data (@tbl-data) is about beaches in Toronto, from @opendatatoronto.
+Here is a preview of the dataset used in this analysis @tbl-data, which spans from 2008 to present.
+The dataset provides a comprehensive overview of key environmental variables observed at Toronto's beaches, including the date of observation, air and water temperatures, rainfall presence, and waterfowl activity.
+These variables are crucial for understanding long-term trends in environmental conditions and their impact on beach safety, water quality, and wildlife behavior.
+This preview serves as an introduction to the dataset's structure and quality, setting the stage for in-depth analysis and trend exploration over time.
 
@@
 ```
-
-This dataset records the date (which was separated into year, month, and day), the air temperature, whether it rains or not, the water temperature, and the observations of water fowls.
-We will analyze the relationship between these variables in the following part.
 

### 2024-09-27 paper/paper.qmd
First Part of Data Completed

@@
 title: "Toronto Beach Data"
-subtitle: "Data Analysis of the Relationship Between Date of Observation, Air Temperatures, Water Temperatures, Rainfall Presence, and waterfowl activity"
+subtitle: "Data Analysis of the Relationship Between Date of Observation, Air Temperatures, Rainfall Presence, Water Temperatures, and Waterfowl Activities"
 author: "Yanzun Jiang"
@@
 
-Here is a preview of the dataset used in this analysis @tbl-data, which spans from 2008 to present.
+The preview of the dataset (@tbl-data) spans from 2008 to present.
 The dataset provides a comprehensive overview of key environmental variables observed at Toronto's beaches, including the date of observation, air and water temperatures, rainfall presence, and waterfowl activity.
@@
 
-### Air Temperature
+### Distribution of the Variables
 
-This histogram (@fig-air-temp) shows the distribution of air temperatures of beaches in Toronto.
+These graphs (@fig-airtemp, @fig-rain, @fig-watertemp, and @fig-waterfowl) visualizes the distribution of air temperatures, rainfall observations, water temperature, and waterfowl observations across the dataset from 2008 to the present.
+These graphs helps identify patterns, outliers, and the overall spread of the data.
+By examining these distributions, we can gain insights into how they behave over time and how it may influence other variables, such as water quality or wildlife observations.
 
 ```{r}
-#| label: fig-air-temp
-#| fig-cap: Air Temperature at Toronto Beaches from
+#| label: fig-airtemp
+#| fig-cap: Distribution of Air Temperature at Toronto Beaches
 #| echo: false
@@
   theme_minimal() +
-  labs(x = "Air Temperature", y = "# of Occurences")
+  labs(x = "Air Temperature (°C)", y = "Frequency")
 ```
-
-We can clearly see the data is unimodal and is not skewed.
-
-### Rain
-
-This bar graph (@fig-rain) shows the distribution of whether it rains of not at beaches in Toronto.
 
@@
 #| label: fig-rain
-#| fig-cap: Bar Graph of Whether It Rains or Not
+#| fig-cap: Rainfall Observations at Toronto Beaches
 #| echo: false
@@
   theme_minimal() +
-  labs(x = "Whether It Rains or Not", y = "# of Occurences")
+  labs(x = "Rainfall Observed", y = "Frequency")
 ```
 
-We can clearly see that there are less raining days.
-
-### Water Temperature
-
-This histogram (@fig-water-temp) shows the distribution of water temperatures of beaches in Toronto.
-
 ```{r}
-#| label: fig-water-temp
-#| fig-cap: Histogram of Water Temperature
+#| label: fig-watertemp
+#| fig-cap: Distribution of Water Temperature at Toronto Beaches
 #| echo: false
@@
   theme_minimal() +
-  labs(x = "Water Temperature", y = "# of Occurences")
+  labs(x = "Water Temperature (°C)", y = "Frequency")
 ```
 
-We can clearly see the data is unimodal, which is the same as air temperatures, but it is left-skewed.
-
-### Observations of Water Fowls
-
-This histogram (@fig-water-fowl) shows the distribution of observations of water fowls of beaches in Toronto.
-
 ```{r}
-#| label: fig-water-fowl
-#| fig-cap: Histogram of Observations of Water Fowls
+#| label: fig-waterfowl
+#| fig-cap: Distribution of Waterfowl Observations at Toronto Beaches
 #| echo: false
@@
   theme_minimal() +
-  labs(x = "Observations of Water Fowls", y = "# of Occurences")
+  labs(x = "Number of Waterfowl Observed", y = "Frequency")
 ```
 
-We can clearly see the data is unimodal but highly right-skewed.
+## Relationships Between the Variables
+
+### Changes of Beaches with Time
+
+These graphs (@fig-time-airtemp-year, @fig-time-rain, @fig-time-watertemp-year, and @fig-time-waterfowl-year) visualize the relationship between each environmental variable and time, spanning from 2008 to the present.
+By plotting air temperature, rainfall observations, water temperature, and waterfowl observations against time, we aim to identify trends, seasonal patterns, and potential long-term changes in these variables at Toronto's beaches.
+Each scatter plot provides insights into how these environmental factors have fluctuated over the years, revealing trends in beach weather conditions and wildlife presence.
+These time-based visualizations will aid in understanding any periodic or gradual changes and their potential impact on beach safety and ecological health.
+
+```{r}
+#| label: fig-time-airtemp-year
+#| fig-cap: Air Temperature Over Time at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = date, y = air_temp)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Date", y = "Air Temperature (°C)")
+```
+
+```{r}
+#| label: fig-time-rain
+#| fig-cap: Rainfall Observations Over Time at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = date, y = rain)) +
+  geom_boxplot(col = "darkblue", fill = "lightblue") +
+  theme_minimal() +
+  labs(x = "Date", y = "Rainfall")
+```
+
+```{r}
+#| label: fig-time-watertemp-year
+#| fig-cap: Water Temperature Over Time at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = date, y = water_temp)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Date", y = "Water Temperature (°C)")
+```
+
+```{r}
+#| label: fig-time-waterfowl-year
+#| fig-cap: Waterfowl Observations Over Time at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = date, y = water_fowl)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Date", y = "Number of Waterfowl Observed")
+```
 
@@
 
-Our results are summarized in.
+From @fig-airtemp, we can clearly see the data is unimodal and is not skewed.
+
+From @fig-rain, we can clearly see that there are less raining days than non-raining days.
+
+From @fig-watertemp, we can clearly see the data is unimodal, which is the same as air temperatures, but it is left-skewed.
+
+From @fig-waterfowl, we can clearly see the data is unimodal but highly right-skewed.
 
@@
 #| message: false
-
-library(rstanarm)
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
@@
 
-The data cleaning process involved renaming variables, filtering out useless columns from the raw dataset, filtering out observations with NAs, and removing the outliers using z-scores.
+The data cleaning process involved renaming variables, tidying the dates, filtering out useless columns from the raw dataset, filtering out observations with NAs, and removing the outliers using z-scores.
 

### 2024-09-27 scripts/00-simulate_data.R
Deleted One Column of Data

@@ -30,7 +30,6 @@ data <-
       origin = "1970-01-01"
     ),
     air_temp = round(rnorm(sim, 20, 5), 2),
-    rain = sample(c("Yes", "No"), sim, p = c(0.35, 0.75), replace = TRUE),
     water_temp = round(rnorm(sim, 15, 4), 2),
     water_fowl = round(rpois(sim, 30))
   )

### 2024-09-27 scripts/02-data_cleaning.R

@@ -21,7 +21,7 @@ cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
   rename(date = data_collection_date) |>
-  select(date, air_temp, rain, water_temp, water_fowl) |>
+  select(date, air_temp, water_temp, water_fowl) |>
   filter_all(all_vars(!is.na(.))) |>
   separate(col = date,
            into = c("year", "month", "day"),
@@ -41,7 +41,6 @@ sd_water_fowl <- sd(cleaned_data$water_fowl)
 cleaned_data <-
   cleaned_data |>
   filter(abs((air_temp - mean_air_temp) / sd_air_temp) < 3,
-         rain == "Yes" | rain == "No",
          abs((water_temp - mean_water_temp) / sd_water_temp) < 3,
          abs((water_fowl - mean_water_fowl) / sd_water_fowl) < 3,
   )

### 2024-09-27 paper/paper.qmd
Changed Format of Cross-Citations

@@
 title: "Toronto Beach Data"
-subtitle: "Data Analysis of the Relationship Between Date of Observation, Air Temperatures, Rainfall Presence, Water Temperatures, and Waterfowl Activities"
+subtitle: "Data Analysis of the Relationship Between Date of Observation, Air Temperatures, Water Temperatures, and Waterfowl Activities"
 author: "Yanzun Jiang"
@@
 thanks: "Code and data supporting this analysis is available at: <https://github.com/Stary54264/Toronto-Beach-Data>"
-abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, rainfall, and waterfowl observations.
+abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, and waterfowl observations.
 The findings reveal that #TODO increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings.# These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
@@
 
-In 2014, Toronto experienced an extremely cold summer that impacted its beaches @torontoweather.
-During this period, data on key environmental factors, such as air temperature, water temperature, rainfall, and observations of waterfowl activity, was collected at various beaches across the city @opendatatoronto.
-These factors are critical as they directly influence the ecological balance of the beaches, the safety of recreational activities, and the overall enjoyment of beachgoers @weatherandbeach.
+In 2014, Toronto experienced an extremely cold summer that impacted its beaches (@torontoweather).
+During this period, data on key environmental factors, such as air temperature, water temperature, and observations of waterfowl activity, was collected at various beaches across the city (@opendatatoronto).
+These factors are critical as they directly influence the ecological balance of the beaches, the safety of recreational activities, and the overall enjoyment of beachgoers (@weatherandbeach).
 
@@
 According to @temperatureandwaterfowl, waterfowl presence can be influenced by temperature changes, precipitation, and human activity on the beaches.
-This study examines the relationships between air temperature, water temperature, rainfall, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.
+This study examines the relationships between air temperature, water temperature, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.
 
@@
 
-The dataset used in this analysis is the "Toronto Beaches Observations" sourced from Toronto's Open Data platform @opendatatoronto.
+The dataset used in this analysis is the "Toronto Beaches Observations" sourced from Toronto's Open Data platform (@opendatatoronto).
 It records various aspects of the beaches in Toronto from 2008 to present.
-In Toronto, water quality at beaches is regularly monitored to ensure public safety, and environmental variables, such as air and water temperature, rainfall, and the presence of waterfowl, are tracked for ecological and recreational purposes @opendatatoronto.
+In Toronto, water quality at beaches is regularly monitored to ensure public safety, and environmental variables, such as air and water temperature, and the presence of waterfowl, are tracked for ecological and recreational purposes (@opendatatoronto).
 
-The variables analyzed in this study include "Date," which records the day each measurement was taken; "Air Temperature," which represents the temperature of the atmosphere at the beach site; "Water Temperature," indicating the temperature of the water in designated swimming areas; "Rainfall," which notes whether there was precipitation on the day of observation; and "Waterfowl Observations," which track the number of birds spotted near the water @opendatatoronto.
+The variables analyzed in this study include "Date," which records the day each measurement was taken; "Air Temperature," which represents the temperature of the atmosphere at the beach site; "Water Temperature," indicating the temperature of the water in designated swimming areas; and "Waterfowl Observations," which track the number of birds spotted near the water (@opendatatoronto).
 
-The dataset was accessed using the `opendatatoronto` package @opendatatoronto.
-For the analysis, the R programming language was employed @citeR, utilizing the `tidyverse` @citetidyverse package for data cleaning, transformation, visualization, and the `janitor` package @citejanitor for initial cleaning and formatting of the raw data.
-Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package @citetidyverse.
+The dataset was accessed using the `opendatatoronto` package (@opendatatoronto).
+For the analysis, the R programming language was employed (@citeR), utilizing the `tidyverse` (@citetidyverse) package for data cleaning, transformation, visualization, and the `janitor` package (@citejanitor) for initial cleaning and formatting of the raw data.
+Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package (@citetidyverse).
 
@@
 The preview of the dataset (@tbl-data) spans from 2008 to present.
-The dataset provides a comprehensive overview of key environmental variables observed at Toronto's beaches, including the date of observation, air and water temperatures, rainfall presence, and waterfowl activity.
+The dataset provides a comprehensive overview of key environmental variables observed at Toronto's beaches, including the date of observation, air and water temperatures, and waterfowl activity.
 These variables are crucial for understanding long-term trends in environmental conditions and their impact on beach safety, water quality, and wildlife behavior.
@@
 
-These graphs (@fig-airtemp, @fig-rain, @fig-watertemp, and @fig-waterfowl) visualizes the distribution of air temperatures, rainfall observations, water temperature, and waterfowl observations across the dataset from 2008 to the present.
+These histograms (@fig-airtemp, @fig-watertemp, and @fig-waterfowl) visualizes the distribution of air temperatures, water temperature, and waterfowl observations across the dataset from 2008 to the present.
 These graphs helps identify patterns, outliers, and the overall spread of the data.
@@
   labs(x = "Air Temperature (°C)", y = "Frequency")
-```
-
-```{r}
-#| label: fig-rain
-#| fig-cap: Rainfall Observations at Toronto Beaches
-#| echo: false
-#| warning: false
-#| message: false
-
-data |>
-  ggplot(aes(x = rain)) +
-  geom_bar(col = "darkblue", fill = "lightblue") +
-  theme_minimal() +
-  labs(x = "Rainfall Observed", y = "Frequency")
 ```
@@
 
-These graphs (@fig-time-airtemp-year, @fig-time-rain, @fig-time-watertemp-year, and @fig-time-waterfowl-year) visualize the relationship between each environmental variable and time, spanning from 2008 to the present.
-By plotting air temperature, rainfall observations, water temperature, and waterfowl observations against time, we aim to identify trends, seasonal patterns, and potential long-term changes in these variables at Toronto's beaches.
+These scatter plots (@fig-year-airtemp, @fig-year-watertemp, and @fig-year-waterfowl) visualize the relationship between each environmental variable and time, spanning from 2008 to the present.
+By plotting air temperature, water temperature, and waterfowl observations against time, we aim to identify trends, and potential long-term changes in these variables at Toronto's beaches.
 Each scatter plot provides insights into how these environmental factors have fluctuated over the years, revealing trends in beach weather conditions and wildlife presence.
@@
 ```{r}
-#| label: fig-time-airtemp-year
-#| fig-cap: Air Temperature Over Time at Toronto Beaches
+#| label: fig-year-airtemp
+#| fig-cap: Air Temperature Over Years at Toronto Beaches
 #| echo: false
@@
 data |>
-  ggplot(aes(x = date, y = air_temp)) +
+  ggplot(aes(x = year, y = air_temp)) +
   geom_point(col = "lightblue") +
   theme_minimal() +
-  labs(x = "Date", y = "Air Temperature (°C)")
+  labs(x = "Year", y = "Air Temperature (°C)")
 ```
@@
 ```{r}
-#| label: fig-time-rain
-#| fig-cap: Rainfall Observations Over Time at Toronto Beaches
+#| label: fig-year-watertemp
+#| fig-cap: Water Temperature Over Years at Toronto Beaches
 #| echo: false
@@
 data |>
-  ggplot(aes(x = date, y = rain)) +
-  geom_boxplot(col = "darkblue", fill = "lightblue") +
+  ggplot(aes(x = year, y = water_temp)) +
+  geom_point(col = "lightblue") +
   theme_minimal() +
-  labs(x = "Date", y = "Rainfall")
+  labs(x = "Year", y = "Water Temperature (°C)")
 ```
@@
 ```{r}
-#| label: fig-time-watertemp-year
-#| fig-cap: Water Temperature Over Time at Toronto Beaches
+#| label: fig-year-waterfowl
+#| fig-cap: Waterfowl Observations Over Years at Toronto Beaches
 #| echo: false
@@
 data |>
-  ggplot(aes(x = date, y = water_temp)) +
+  ggplot(aes(x = year, y = water_fowl)) +
   geom_point(col = "lightblue") +
   theme_minimal() +
-  labs(x = "Date", y = "Water Temperature (°C)")
+  labs(x = "Year", y = "Number of Waterfowl Observed")
 ```
 
+These scatter plots (@fig-month-airtemp, @fig-month-watertemp, and @fig-month-waterfowl) illustrate the seasonal variations in air temperature, water temperature, rainfall occurrence, and waterfowl observations at Toronto beaches from 2008 to the present.
+By plotting these variables over time, distinct seasonal patterns emerge, with warmer temperatures and higher waterfowl activity typically observed during the summer months, and cooler temperatures in winter.
+The scatter plots help visualize how these environmental factors fluctuate throughout the year, reflecting natural seasonal cycles.
+Observing these recurring trends provides valuable insights into the seasonal dynamics affecting beach ecosystems and recreational conditions.
+
 ```{r}
-#| label: fig-time-waterfowl-year
-#| fig-cap: Waterfowl Observations Over Time at Toronto Beaches
+#| label: fig-month-airtemp
+#| fig-cap: Seasonal Change of Air Temperature at Toronto Beaches
 #| echo: false
@@
 data |>
-  ggplot(aes(x = date, y = water_fowl)) +
+  ggplot(aes(x = month, y = air_temp)) +
   geom_point(col = "lightblue") +
   theme_minimal() +
-  labs(x = "Date", y = "Number of Waterfowl Observed")
+  labs(x = "Month", y = "Air Temperature (°C)")
+```
+
+```{r}
+#| label: fig-month-watertemp
+#| fig-cap: Seasonal Change of Water Temperature at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = month, y = water_temp)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Month", y = "Water Temperature (°C)")
+```
+
+```{r}
+#| label: fig-month-waterfowl
+#| fig-cap: Seasonal Change of Waterfowl Observations at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = month, y = water_fowl)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Month", y = "Number of Waterfowl Observed")
 ```
@@
 From @fig-airtemp, we can clearly see the data is unimodal and is not skewed.
-
-From @fig-rain, we can clearly see that there are less raining days than non-raining days.
 

### 2024-09-27 paper/paper.qmd
Part 2 Completed

@@
 
-### Preview of the Dataset
+## Preview of the Dataset
 
@@
 
+## Data Visualization
+
 ### Distribution of the Variables
 
-These histograms (@fig-airtemp, @fig-watertemp, and @fig-waterfowl) visualizes the distribution of air temperatures, water temperature, and waterfowl observations across the dataset from 2008 to the present.
+These histograms (@fig-air, @fig-water, and @fig-fowl) visualizes the distribution of air temperatures, water temperature, and waterfowl observations across the dataset from 2008 to the present.
 These graphs helps identify patterns, outliers, and the overall spread of the data.
@@
 ```{r}
-#| label: fig-airtemp
+#| label: fig-air
 #| fig-cap: Distribution of Air Temperature at Toronto Beaches
@@
 ```{r}
-#| label: fig-watertemp
+#| label: fig-water
 #| fig-cap: Distribution of Water Temperature at Toronto Beaches
@@
 ```{r}
-#| label: fig-waterfowl
+#| label: fig-fowl
 #| fig-cap: Distribution of Waterfowl Observations at Toronto Beaches
@@
 
-## Relationships Between the Variables
-
 ### Changes of Beaches with Time
 
-These scatter plots (@fig-year-airtemp, @fig-year-watertemp, and @fig-year-waterfowl) visualize the relationship between each environmental variable and time, spanning from 2008 to the present.
+These scatter plots (@fig-year-air, @fig-year-water, and @fig-year-fowl) visualize the relationship between each environmental variable and time, spanning from 2008 to the present.
 By plotting air temperature, water temperature, and waterfowl observations against time, we aim to identify trends, and potential long-term changes in these variables at Toronto's beaches.
@@
 ```{r}
-#| label: fig-year-airtemp
+#| label: fig-year-air
 #| fig-cap: Air Temperature Over Years at Toronto Beaches
@@
 ```{r}
-#| label: fig-year-watertemp
+#| label: fig-year-water
 #| fig-cap: Water Temperature Over Years at Toronto Beaches
@@
 ```{r}
-#| label: fig-year-waterfowl
+#| label: fig-year-fowl
 #| fig-cap: Waterfowl Observations Over Years at Toronto Beaches
@@
 
-These scatter plots (@fig-month-airtemp, @fig-month-watertemp, and @fig-month-waterfowl) illustrate the seasonal variations in air temperature, water temperature, rainfall occurrence, and waterfowl observations at Toronto beaches from 2008 to the present.
-By plotting these variables over time, distinct seasonal patterns emerge, with warmer temperatures and higher waterfowl activity typically observed during the summer months, and cooler temperatures in winter.
+These scatter plots (@fig-month-air, @fig-month-water, and @fig-month-fowl) illustrate the seasonal variations in air temperature, water temperature, rainfall occurrence, and waterfowl observations at Toronto beaches from 2008 to the present.
+By plotting these variables over time, distinct seasonal patterns emerge.
 The scatter plots help visualize how these environmental factors fluctuate throughout the year, reflecting natural seasonal cycles.
@@
 ```{r}
-#| label: fig-month-airtemp
+#| label: fig-month-air
 #| fig-cap: Seasonal Change of Air Temperature at Toronto Beaches
@@
 ```{r}
-#| label: fig-month-watertemp
+#| label: fig-month-water
 #| fig-cap: Seasonal Change of Water Temperature at Toronto Beaches
@@
 ```{r}
-#| label: fig-month-waterfowl
+#| label: fig-month-fowl
 #| fig-cap: Seasonal Change of Waterfowl Observations at Toronto Beaches
@@
 
-# Results {#sec-results}
+### Correlations Between Observed Variables
 
-From @fig-airtemp, we can clearly see the data is unimodal and is not skewed.
-
-From @fig-watertemp, we can clearly see the data is unimodal, which is the same as air temperatures, but it is left-skewed.
-
-From @fig-waterfowl, we can clearly see the data is unimodal but highly right-skewed.
+These scatter plots (@fig-air-water, @fig-water-fowl) explore the relationships between various observed variables, such as air temperature, water temperature, and waterfowl observations, to identify potential correlations.
+By plotting some variables against some other, we aim to uncover how these environmental factor might influence another.
+For instance, the relationship between air temperature and water temperature may reveal patterns in heat transfer between the atmosphere and water, while the correlation between water temperature and waterfowl observations could indicate how weather conditions affect wildlife activity.
+These scatter plots provide a deeper understanding of the interconnectedness of these variables and offer insights into how environmental conditions at Toronto beaches influence each other.
 
 ```{r}
+#| label: fig-air-water
+#| fig-cap: Relationship Between Air Temperature and Water Temperature at Toronto Beaches
 #| echo: false
-#| eval: true
 #| warning: false
@@
 
+data |>
+  ggplot(aes(x = air_temp, y = water_temp)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Air Temperature (°C)", y = "Water Temperature (°C)")
 ```
+
+```{r}
+#| label: fig-water-fowl
+#| fig-cap: Relationship Between Water Temperature and Waterfowl Observations at Toronto Beaches
+#| echo: false
+#| warning: false
+#| message: false
+
+data |>
+  ggplot(aes(x = water_temp, y = water_fowl)) +
+  geom_point(col = "lightblue") +
+  theme_minimal() +
+  labs(x = "Water Temperature (°C)", y = "Number of Waterfowl Observed")
+```
+
+# Results {#sec-results}
+
+## Gain from Distribution of the Variables
+
+The histogram of air temperatures, as shown in @fig-air, reveals that most recorded air temperatures at Toronto beaches fall between 12°C and 30°C, with a noticeable peak around 20°C.
+The distribution is approximately symmetric, indicating no significant skew, meaning that air temperatures are evenly spread around the central value.
+This suggests that beach monitoring predominantly occurs during periods of moderate and comfortable weather, which is conducive to outdoor activities.
+Temperatures below 8°C and above 33°C are much less frequent, indicating that extreme weather conditions are rare, emphasizing the temperate climate in Toronto during beach usage periods.
+
+In contrast, the water temperature histogram, seen in @fig-water, is left-skewed, meaning that while most temperatures cluster between 8°C and 25°C, there is a tail extending toward lower temperatures.
+A peak is observed around 18°C, representing the most common water temperatures during beach season.
+The left skew indicates that colder water temperatures are infrequent but present, typically occurring outside peak summer months.
+This distribution reflects how water retains heat more slowly than air, remaining relatively cool even as air temperatures rise, which is characteristic of large bodies of water.
+
+Lastly, the waterfowl observations histogram, as seen in @fig-fowl, displays a highly right-skewed distribution.
+Most days had a low count of waterfowl, with the majority of observations falling between 0 and 50 observations.
+However, a long tail extends to the right, indicating that while large counts of waterfowl are rare, they do occur on certain days.
+This right skew suggests occasional spikes in bird activity, possibly linked to seasonal migrations or environmental conditions that attract more birds to the beaches.
+These sporadic peaks could have implications for water quality, as larger groups of waterfowl might increase the risk of contamination.
+
+These histograms (@fig-air, @fig-water, and @fig-fowl) offer valuable insights into the key environmental variables affecting Toronto beaches.
+The symmetric air temperature distribution, left-skewed water temperature, and highly right-skewed waterfowl observations each reveal distinct patterns that inform public health monitoring and beach management decisions, ensuring that the environment remains safe and enjoyable for visitors.
+
+## Gain from Changes of Beaches with Time
 

### 2024-09-27 paper/paper.qmd
3.2 Completed

@@
 
+@fig-year-air shows the relationship between air temperature and time.
+Over the years, we observe a decrease followed by an increase in air temperatures, with potential gradual trends reflecting long-term changes rather than distinct seasonal cycles.
+This could indicate climate-related variations or other long-term environmental shifts affecting the air temperature at the beaches.
+
+@fig-year-water displays water temperature versus time.
+Similar to air temperature, water temperature shows fluctuations across years, but with a less explicit pattern.
+The data suggests that the overall trends could be linked to climate change or weather anomalies.
+
+@fig-year-fowl illustrates waterfowl observations over time.
+The scatter plot reveals variations in bird activity across different years.
+While no sharp seasonal patterns are apparent due to the yearly scale, the data might point toward longer-term changes in waterfowl populations, potentially related to environmental factors, habitat changes, or migratory patterns.
+
+These scatter plots (@fig-year-air, @fig-year-water, and @fig-year-fowl) provide an overview of how the environmental conditions at Toronto beaches have evolved over the years.
+Rather than focusing on short-term seasonal changes, these visualizations highlight potential long-term trends and environmental shifts that could have significant implications for beach management and ecosystem health.
+
+## Gain from Seasonal Changes of Beaches
+
 # Discussion {#sec-discussion}

### 2024-09-27 paper/paper.qmd
Part 3 Completed

@@
 
+@fig-month-air illustrates the relationship between air temperature and time, focusing on the months from May to October.
+A clear seasonal pattern emerges, with air temperatures gradually increasing from May, peaking around July, and then declining into September.
+The seasonal cycle is evident, as air temperatures warm up in late spring, reach their highest points in midsummer, and cool down as fall approaches.
+This reinforces the influence of seasonal climate variations on beach conditions.
+
+@fig-month-water presents air temperature versus time over the same period.
+It reveals a similar pattern to air temperature, with a peak in August, which is later than air temperature.
+This might be due to the absorption of heat in water, causing the temperature to fall gradually.
+This trend aligns with typical summer weather patterns, where water temperatures rise due to prolonged exposure to sunlight and warmer air, creating optimal conditions for beachgoers.
+
+@fig-month-fowl depicts waterfowl observations versus months from May to September.
+It shows varying levels of bird activity throughout the summer months, with peaks in July or August.
+These fluctuations could be influenced by breeding seasons, availability of food, or migratory behavior, all of which are affected by seasonal changes.
+The variability in bird counts reflects how environmental factors and beach conditions interact with wildlife throughout the warmer months.
+
+In summary, these scatter plots (@fig-month-air, @fig-month-water, and @fig-month-fowl) highlight the clear seasonal trends in both temperature and waterfowl observations at Toronto beaches between May and September.
+These patterns are important for understanding how environmental conditions shift during the beach season and inform management strategies for maintaining water quality and ecosystem balance during peak usage times.
+
+## Gain from Correlations Between Observed Variables
+
+@fig-air-water depicts the relationship between air temperature and water temperature.
+It shows a clear positive correlation between the two variables: as air temperatures rise, water temperatures also tend to increase.
+This relationship is expected, as higher air temperatures lead to more intense solar radiation and warming of the water.
+However, the variance of water temperature given same air temperature is large.
+There might be other confounders affecting this relationship.
+Also, this might be due to the slower rate at which water heats and cools compared to air.
+
+@fig-water-fowl illustrates the relationship between water temperature and waterfowl observations.
+It does not show a linear relationship between the variables.
+Rather, it reveals that waterfowl counts are generally higher when water temperatures are moderate, with fewer birds observed at the extreme ends of the temperature range.
+This suggests that waterfowl may be more active or present in larger numbers when water conditions are neither too cold nor too warm, possibly reflecting optimal conditions for feeding or habitat usage during these periods.
+
+These scatter plots (@fig-air-water and @fig-water-fowl) help clarify how environmental variables at Toronto beaches are interrelated.
+The strong correlation between air and water temperatures demonstrates how weather patterns influence beach conditions, while the relationship between water temperature and waterfowl observations provides insights into how wildlife activity is shaped by environmental factors.
+Understanding these connections is crucial for managing beach environments and ensuring both human and ecological health.
+
 # Discussion {#sec-discussion}

### 2024-09-27 paper/paper.qmd
Added Summarise Statistics to Appendix

@@
 
+## Summary Statistics of the Data
+
+The summary statistics provides key statistical insights into the environmental variables analyzed at Toronto beaches.
+For each variable, the summarize tables (@tbl-summarise-air, @tbl-summarise-water, and @tbl-summarise-fowl) reports the mean, median, variance, minimum value, maximum value, and interquartile range of those vairables, offering a concise overview of range, central tendencies, and variability in the data.
+
+```{r}
+#| label: tbl-summarise-air
+#| tbl-cap: Summarise Statistics of Air Temperatures
+#| echo: false
+#| warning: false
+#| message: false
+
+summarise_air_temp <- data |>
+  summarise(Mean = mean(air_temp),
+            Median = median(air_temp),
+            Variance = var(air_temp),
+            Min = min(air_temp),
+            Max = max(air_temp),
+            IQR = IQR(air_temp)
+  )
+kable(summarise_air_temp, format = "markdown")
+```
+
+```{r}
+#| label: tbl-summarise-water
+#| tbl-cap: Summarise Statistics of Water Temperatures
+#| echo: false
+#| warning: false
+#| message: false
+
+summarise_water_temp <- data |>
+  summarise(Mean = mean(water_temp),
+            Median = median(water_temp),
+            Variance = var(water_temp),
+            Min = min(water_temp),
+            Max = max(water_temp),
+            IQR = IQR(water_temp)
+  )
+kable(summarise_water_temp, format = "markdown")
+```
+
+```{r}
+#| label: tbl-summarise-fowl
+#| tbl-cap: Summarise Statistics of Waterfowl Observations
+#| echo: false
+#| warning: false
+#| message: false
+
+summarise_water_fowl <- data |>
+  summarise(Mean = mean(water_fowl),
+            Median = median(water_fowl),
+            Variance = var(water_fowl),
+            Min = min(water_fowl),
+            Max = max(water_fowl),
+            IQR = IQR(water_fowl)
+  )
+kable(summarise_water_fowl, format = "markdown")
+```
+
 \newpage

### 2024-09-27 paper/paper.qmd
Updated Findings in Abstract and Introduction

@@
 abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, and waterfowl observations.
-The findings reveal that #TODO increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings.# These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
+The findings reveal that air temperatures have a linear relationship with water temperatures, while increased water temperatures correlate with higher waterfowl activity in some content.
+These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly.
 Future research should explore the impact of these environmental factors on beachgoer experiences and the broader ecological implications."
@@
 To conduct this analysis, a dataset collected by @opendatatoronto was utilized, as described in @sec-data.
-Based on the initial findings, it was observed that #TODO higher water temperatures coincided with an increase in waterfowl activity, while rainy days led to a decrease in sightings (@sec-results).# As discussed in @sec-discussion, #TODO these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness.
+Based on the initial findings, it was observed that higher air temperatures are correlated with higher water temperatures, while higher water temperatures coincided with an increase in waterfowl activity in some extent(@sec-results).
+As discussed in @sec-discussion, #TODO these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness.
 Further recommendations include improving public awareness of how wildlife interactions and weather patterns influence beach environments.# This paper's structure includes an overview of the data and methods in @sec-data, the results of the analysis in @sec-results, a detailed discussion of the results in @sec-discussion, and supplementary insights in @sec-appendix.

### 2024-09-27 paper/paper.qmd
Added Measurement Part in Data

@@
 Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package (@citetidyverse).
+
+## Measurement
+
+Each variable in this dataset was measured with specific techniques that ensure accuracy and relevance to the analysis of Toronto beaches.
+
+Air temperatures were measured using calibrated thermometers placed in shaded areas to avoid direct sunlight, providing accurate readings of the ambient temperature.
+Measurements were taken at regular intervals throughout the day, typically during peak observation hours, to capture variations in temperature across different times (@measurement).
+
+Water temperature was recorded using submerged thermometers positioned at varying depths.
+This approach allowed for capturing temperature gradients that could occur in different water layers, offering insights into thermal stratification, especially during warmer months (@measurement).
+
+Observations of waterfowl were conducted using a standardized counting method and estmating method.
+Trained observers recorded the number of birds present at various times throughout the day, ensuring that counts were conducted under similar conditions to minimize variability.
+Then they use the samples to estimate the total number of waterfowls.
+This method also included recording species, which adds valuable information about the biodiversity present in the area (@opendatatoronto).
+
+By discussing these measurement techniques, we establish a clear connection between the dataset and the reliability of the results.
+This thorough exploration of measurement practices highlights the importance of consistent and accurate data collection in understanding the environmental dynamics of Toronto beaches.
 
